Data Exploration: IUCN and AquaMaps

### 2016-09-14 clip_depth/coral_maps.Rmd
bumping up text size on figures

map_coral_comp <- 
  tm_shape(rast_coral_comp) +
    tm_raster(breaks = c(0, 200, Inf),
              palette = c('lightblue', 'royalblue4'),
              colorNA = NULL,
              title = 'depth (meters)',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            legend.text.size = .5,
            legend.title.size = .6,
            # title.position = 'TOP', 
            legend.outside = FALSE, 
            legend.position = c('left', 'bottom'),
            legend.bg.color = 'white',
            legend.bg.alpha = .5,
            attr.outside = TRUE)

>>>>

map_coral_comp <- 
  tm_shape(rast_coral_comp) +
    tm_raster(breaks = c(0, 200, Inf),
              palette = c('lightblue', 'cyan4'),
              colorNA = NULL,
              title = 'depth (meters)',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            legend.text.size = .8,
            legend.title.size = .9,
            # title.position = 'TOP', 
            legend.outside = FALSE, 
            legend.position = c('left', 'bottom'),
            legend.bg.color = 'white',
            legend.bg.alpha = .5,
            attr.outside = TRUE)
